### 2021-06-09 paper/medical_parameters.tex
Add some references. Address some of HM's comments. Not running through. Probably missing curly bracket somewhere.
Fix reference unicode error. Minor improvements to the medical parameters.

\subsection{Medical Parameters}

@@

% Length of the presymptomatic stage
The \href{European Centre for Disease Prevention and Control}{https://bit.ly/3pi18Ax}
reports that people become infectious between one and two days before symptoms start.\footnotemark

\footnotetext{
This is similar to \citet{He2020} and in line with
\citet{Peak2020}.}

@@

For symptomatic cases they arrive at 0-5 days before symptom onset (figure 2) and 3-8
days of infectiousness afterwards.\footnotemark Thus, we arrive at 0 to 13 days as the
range for infectiousness among individuals who become symptomatic (see also figure 5).
This duration range is very much in line with the meta-analysis’ reported evidence for
asymptomatic individuals (see their figure 1).

\footnotetext{
    Viral loads may be detected much later but 8 days seems to be the time after which
    most people are culture negative, as also reported by \citet{Singanayagam2020}.
}

Following this evidence we assume the following discretized distribution of the
infectiousness period: 10\% of individuals are infectious for three days, 25\% for five
days, another 25\% for seven days, 20\% for nine days and 20\% for eleven days.

@@

We collapse the data to the following distribution: 10\% recover after 15 days and 30\%
require 18, 22 or 27 days respectively.

>>>>

\subsection{Medical Parameters}
\label{sec:medical_params}

@@

% Length of the presymptomatic stage
The \href{https://bit.ly/3pi18Ax}{European Centre for Disease Prevention and Control}
reports that people become infectious between one and two days before symptoms
start.\footnotemark

\footnotetext{This is similar to \citet{He2020} and in line with \citet{Peak2020}.}

@@

For symptomatic cases they arrive at zero to five days before symptom onset (figure 2)
and three to eight days of infectiousness afterwards.\footnotemark Thus, we arrive at 0
to 13 days as the range for infectiousness among individuals who become symptomatic (see
also figure 5).

\footnotetext{Viral loads may be detected much later but eight days seems to be the time
    after which most people are culture negative, as also reported by
    \citet{Singanayagam2020}.}

@@
